Essays in \\Computational Management Science

### 2018-01-17 FrontBackmatter/Introduction.tex
Introduction

%*******************************************************
% Publications
%*******************************************************
\pdfbookmark[1]{Prelude}{prelude}
\chapter*{Prelude, introduction, and discussion of a thesis proposal}
\bigskip

\noindent If anything good can ever be said about the second world war, it might be this: the war effort sparked a massive number of scientific fields.

@@

Applied mathematics and computer science serve simultaneously as a theoretical foundation and the major tool available to the field.  Though this is a thesis proposal concerning business, in this document one should expect to find the language and nomenclature of mathematical modeling and computer science as our primary and most natural language.

This proposal will present a number of different topics for exploration. Though the range of the topics is large, as it usually is in management science, it is my hope to convince readers of the value of a future thesis brought by three self-contained scientific papers. %---of the kind and quality that is expected in the major scientific journals of the field.

%Though work has already begun in all of these studies, at this moment, for the proposal, each study is offered under its own  level of maturity, ranging from quasi-ready for submission for publication to research at its embryonic phase.

The first paper lies at the intersection of computer science, record-keeping, banking \& finance, and economic inclusion. Our concern will be over a Bitcoin-like system that departs from the blockchain architecture. It has been recently proposed that Directed Acyclic Graphs could certify transactions in a blockchain-like manner.  We investigate some issues regarding this possibility, namely: (i) cryptographic security and game-theoretical attacks; (ii) scalability; (iii) self-governance of the system; (iv) appropriate incentive system to all participants.

%This first paper is the most immature one.  It is work being conducted.  The research questions are still under consideration. Some original theorems (yet to be proved) are presented.  
This first paper is work being conducted. The research questions are still under consideration. Some original theorems (yet to be proved) are presented.

@@

>>>>

\documentclass[12pt]{article}

\usepackage{natbib}

%% Language and font encodings
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}

%% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

\title{Essays in \\Computational Management Science}
\author{Marcelo Salhab Brogliato}

\begin{document}
\maketitle

\section{Introduction}

If anything good can ever be said about the second world war, it might be this: the war effort sparked a massive number of scientific fields.

@@

Applied mathematics and computer science serve simultaneously as a theoretical foundation and the major tool available to the field.  Though this is a doctoral thesis concerning business, in this document one should expect to find the language and nomenclature of mathematical modeling and computer science as our primary and most natural language.

This thesis will present a number of different topics for exploration. Though the range of the topics is large, as it usually is in management science, it is my hope to convince readers of the value of this doctoral thesis brought by three self-contained scientific papers.  The first of which will study the possibility of distributed financial ledgers.

\subsection{Distributed financial ledgers}

United Nations World Food Programme, `Blockchain Against Hunger: Harnessing Technology In Support Of Syrian Refugees', 30 May 2017, https://www.wfp.org/news/news-release/blockchain-against-hunger-harnessing-technology-support-syrian-refugees, accessed in January 17, 2018.

United Nations World Food Programme, 2016, The Year in Review Report, p.

The first paper lies at the intersection of computer science, record-keeping, banking \& finance, and economic inclusion. The seminal work of \citet{nakamoto2008bitcoin} described the architecture of Bitcoin, a peer-to-peer electronic cash system, also known as cryptocurrency. Bitcoin's currency ledger is public and stored in a blockchain across thousands of computers. Even so, no one is able to spend either somebody else's funds nor to double spend their own funds. In order to be confirmed, each transaction must be both digitally signed by the owner of the money and the funds verified in the blockchain by Bitcoin's miners. One of the interesting parts of Bitcoin are the incentives. On one hand, users have incentive to use Bitcoin because the fees are small, the money transfer is quick, and the currency issuance rate is well known. On the other hand, the miners have incentive to be part of Bitcoin's network because new coins are found every ten minutes.

The impact of Bitcoin in society -- and hence in the companies and the government -- has been increasing every day. People are increasingly using Bitcoin to exchange money and transfer money overseas. Companies are looking into Bitcoin as an alternative to reduce banking fees. The poor may be included in the finance system through Bitcoin. People may hedge their assets against their governments' money issuance and inflation---as in the sad case of Venezuela.

Bitcoin is the first and most famous cryptocurrency, used worldwide and has a highly volatile market cap, as of this writing, of \$ 224 mi. Even so, it faces serious scalability challenges; such as serious quality of service and network congestion when the number of transactions per second is high, and an increase in the transaction fees and uncertain delays in transactions' confirmations.

Note that these problems have been a deliberate decision from the current developers of the ``bitcoin-core'' developers, which believe that is it risky to increase the the blocksize (in which all transactions are stored).  It is not known whether a blocksize, say, of 1Gb, would be feasible to sustain the decentralization of the network.

Iota is another cryptocurrency, but, instead of using a blockchain, it proposes the use a ``tangle' architecture', which is a different way to store the currency ledger across thousands of computers. Although it has not been confirmed in practice yet, its architecture seems to be significantly more scalable than Bitcoin's blockchain. As we will see, the problem here is exactly the opposite of Bitcoin's. It needs a minimum of transactions per seconds in order to work properly.

Our analysis suggests an architecture for a distributed currency which is inspired in both Bitcoin's blockchain and Iota's tangle in order to solve the scalability problems. While Bitcoin's network saturates when it hits a certain number of transactions per second, Iota's does not work properly with less than a certain number of transactions per second. Our proposed architecture works in both scenarios: low and high number of transactions per second.

We investigate some issues regarding this possibility, namely: (i) cryptographic security and game-theoretical attacks; (ii) scalability; (iii) self-governance of the system; (iv) appropriate incentive system to all participants.

\subsection{Sparse Distributed Memory}

@@

\bibliographystyle{apa}
\bibliography{sample.bib}
\end{document}
